Estimating Body Fat Using Circumference Measurements

### 2024-11-26 paper/paper.qmd
updated references

@@

This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car]. The dataset used in this study, sourced from The Data And Story Library [@dasl], contains measurements on body fat percentage alongside various physical metrics for 250 male participants. The dataset was collected to analyze body fat as an important health measure, providing variables such as age, weight, height, and circumferences of specific body parts. These measurements were obtained through direct assessments to ensure accuracy and uniform input into the dataset. The dataset allows researchers to consider accessible ways to estimate body fat without relying on costly or specialized methods.

>>>>

This study uses the statistical programming language R [@citeR] and the packages: tidyverse  [@tidyverse], Arrow [@arrow], MASS [@mass], GGally [@ggally], gridExtra [@gridextra], Knitr [@knitr], kableExtra [@kableextra], Car [@car], TestThat [@testthat], dplyr [@dplyr], readr [@readr], tidyr [@tidyr].

@@

The dataset used in this study, sourced from The Data And Story Library [@dasl], contains measurements on body fat percentage alongside various physical metrics for 250 male participants. The dataset was collected to analyze body fat as an important health measure, providing variables such as age, weight, height, and circumferences of specific body parts. These measurements were obtained through direct assessments to ensure accuracy and uniform input into the dataset. The dataset allows researchers to consider accessible ways to estimate body fat without relying on costly or specialized methods.
